Evaluation of dynamic resource allocation strategies for overlay Apache Spark clusters on HPC

### 2019-05-02 paper.tex
updated cedar figures, bug fixes to figure generation script and changes to intro

Pilot scheduling has been applied to scientific workflow engines including Pegasus,
PSOM and RADICAL-Pilot. While there have been some efforts on implementing pilot scheduling
approaches for \cite{jha and spark on pbs paper}. However, these projects are either
not open-source or not necessarily compatible with Slurm.

Here we present SPA, a pilot-scheduling library for launching Spark applications 
on HPC infrastructures. This library currently enables the launching of Spark applications
on Slurm-based clusters by dividing the total amount of resources required and requesting
multiple instances of subsets of the resources at a time. When a single 
instance is started, a Standalone Spark cluster is started. Built-in 
fault-tolerance of Spark masters and workers is leveraged, in addition 
to Driver fault tolerance for Scala-based applications. When nodes are 
lost due to walltime expiration, additional pilot nodes are launched 
until the driver completes. SPA facilitates the execution of large 
neuroimaging Spark applications on HPC systems.

>>>>

Pilot scheduling techniques have already been applied to scientific workflow engines, such as
Pegasus, PSOM and RADICAL-Pilot~\cite{}. While there have been some efforts on
implementing pilot scheduling approaches for Apache Spark\cite{jha and spark on pbs paper},
research is limited and none of the them detail the effects of an overlay cluster
on overall performance and robustness.

In this paper, we will analyse the effects of pilot scheduling strategies with an 
overlay Spark cluster. Our evaluation will be broken down into two parts: 1)
the overall added value of pilots, and 2), tolerance to failures. Part 1 will 
investigate the effect of queuing times on pilot applications. 
Here we present SPA, a pilot-scheduling library for launching Spark applications 
on HPC infrastructures. This library currently enables the launching of Spark applications
on Slurm-based clusters by dividing the total amount of resources required and requesting
multiple instances of subsets of the resources at a time. When a single 
instance is started, a Standalone Spark cluster is started. Built-in 
fault-tolerance of Spark masters and workers is leveraged, in addition 
to Driver fault tolerance for Scala-based applications. When nodes are 
lost due to walltime expiration, additional pilot nodes are launched 
until the driver completes. SPA facilitates the execution of large 
neuroimaging Spark applications on HPC systems.
